---
title: "A Shiny App that shows Miles per Gallon Relationship with Other Variables"
author: "Bamidele Tella"
date: "7th of January, 2021"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(shiny)
library(datasets)
library(png)
```

## Overview
This is a shiny application project for the Coursera's Developing Data Products. We make use of Motor Trend Data, a magazine containing Data about the automobile industry looking at a data set of a collection of cars, We are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). Under this analysis, we can answer the question: Is an automatic or manual transmission better for MPG,by quantify the MPG difference between automatic and manual transmissions, among other analysis that can be conducted. It contains a Boxplot of Fitted Model, a line indicating the model on a plot of MPG vs an input Variable, it also shows the Summary of the Model. The app is divided into two parts: User Interface(UI) and Server which serves as the engine of the application.

## User Interface Source Code(UI)
```{r, echo=TRUE,eval=FALSE}
shinyUI(
    fluidPage(
        titlePanel("An App that shows the relationship of Miles per Gallon to different Variables"),
            sidebarLayout(
                sidebarPanel(
                    selectInput("variable","Varables:",
                                c("Number of Cylinder"="cyl",
                                  "Displacement"="disp",
                                  "HorsePower"="hp",
                                  "Rear Axle Ratio"="drat",
                                  "Weight"="wt",
                                  "1/4 Mile Time"="qsec",
                                  "Engine"="vs",
                                  "Transmission"="am",
                                  "Number of Fward Gears"="gear",
                                  "Number of Carburetors"="carb"
                                  )
                                ),
                    checkboxInput("outliers", "Show Plot's Outliers", FALSE),
                    submitButton("Submit!")
                    
                    ),
                
                mainPanel(
                    h2(textOutput("caption")),
                    tabsetPanel(type = "tabs",
                                tabPanel("BoxPlot", plotOutput("airbox")),
                                tabPanel("Regression Model", 
                                         plotOutput("airplot"),
                                         verbatimTextOutput("airfit")
                                         )
                                )
                    )
                )
        )
    )
```

## Server Source Code
```{r, eval=FALSE,echo=TRUE}
mpgData=mtcars
mpgData$am = factor(mpgData$am, labels = c("Automatic","Manual"))

shinyServer(function(input, output) {
   
     airformula = reactive({
        paste("mpg ~", input$variable)
    })
    
    airpoint = reactive({
        paste("mpg ~", "as.integer(",input$variable,")")
    })
    
    airfit = reactive({
        lm(as.formula(airpoint()),data = mpgData)
    })
    
    output$caption = renderText({
        airformula()
    })
    
    output$airbox = renderPlot({
        boxplot(as.formula(airformula()), data = mpgData, outline = input$outliers)
    })
    output$airfit = renderPrint({
        summary(airfit())
        })
    output$airplot = renderPlot({
        with(mpgData, {
            plot(as.formula(airpoint()))
            abline(airfit(),col="blue")
        })
    })
    
})

```

## App Images
```{r}
d1 <- readPNG("d1.png")
plot.new()
rasterImage(d1,0,0,1,1)

d2 <- readPNG("d2.png")
plot.new()
rasterImage(d2,0,0,1,1)

d3 <- readPNG("d3.png")
plot.new()
rasterImage(d3,0,0,1,1)
```


